---
title: "Sea Surface Temperature (SST) Report"
subtitle: "Project: STRETCH"
author: "Author: Dana K Briscoe"
date: 'Report Date: `r Sys.Date()`'
output: 
  html_document:
    style: "style.css"
params:
  eov: "sst"
  eov_unit: "°C"
  deploy_lons: !r c(-160, -150, -145, -140) 
  interval: "weekly"
  sst_thresh: !r c(17)
  enddate: !r Sys.Date() - 1
  startdate: !r params$enddate - 15
  add_clim: TRUE
  add_sst_map: TRUE
  save_rds: FALSE
  nc_path: "/Users/briscoedk/dbriscoe@stanford.edu - Google Drive/My Drive/ncdf/deploy_reports"
---

<style>
.main-container {
    max-width: 1180px;
    margin-left: 10;
    margin-right: 10;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    eval = TRUE,
    message = FALSE,
    warning = FALSE,
    dpi = 300,
    fig.align = "center"
    )

# See Options: knitr::opts_chunk$get()
```

```{r load-libraries}
# Load Libraries ---
library(tidyverse)
library(lubridate)
library(raster)
library(sf)
library(plotly)
library(ggthemes)

```

```{r source-helper-funcs}
## Source helper functions
source('00_automate_SST_helper_functions.R')
```

```{r list-ncs}
# 1) get nc dir
ncs <- list.files(params$nc_path, pattern = params$eov, full.names=T)

```

```{r get-date-range}
## only for unit testing ---
fdates <- ncs %>% 
  str_split(., "_") %>%
    purrr::map_chr(~ pluck(., 5)) %>%
    substr(., start=1, stop=10)

# params$startdate = fdates[1]
# params$startdate = fdates[length(fdates)]

## end only for unit testing ---
dates = fdates
# dates <- getDateRange(params$startdate, params$enddate, unit = 'day')

```

```{r get-ncs-by-date}
# pull new ncdf by dates
ncIn <- sapply(1:length(dates), function(x) ncs[grepl(dates[x],ncs)])

```

```{r nc-to-raster-stack}
# convert ncs to raster stack
ras <- raster::stack(ncIn)

ras <- setZ(ras, ncIn %>% 
    map_chr(~parseDT(., start=13, stop = 22, format="%Y-%m-%d")) %>%
    as.Date(), name = 'date') 

# name raster layers (select one)
names(ras) <- tools::file_path_sans_ext(basename((ncIn)))
names(ras) <- str_c('daily_sst_', getZ(ras))

# 5 save as .grid in another dir??

```

```{r get-shipping-route-coords}
Port_Yokohama = c(139.997,34.673)
Port_SanLazaro_Cardenas = c(-111.738, 22.750)
   
ship_route_pts <- get_shipping_route(port_start = Port_Yokohama, port_end = Port_SanLazaro_Cardenas, lon_type = "360") #%>% mutate(across(everything(), round, 0))

```

```{r pull-xycoords-for-ts}
# locate possible deploy lons along shipping route
lons_idx = sapply(1:length(params$deploy_lons), function(x) {findInterval(make360(params$deploy_lons)[x], ceiling(make360(ship_route_pts$lon)), rightmost.closed  = TRUE)})

# pull coords for timeseries
xy <- ship_route_pts %>%
    slice(lons_idx) %>%
    # mutate(across(everything(), ceiling)) %>%   ## note: you'd think you'd use floor, but it's neg, so use ceiling to round down
    setNames(c('x', 'y'))

```


```{r set-cpal}
# based on specific lons & length of params$deploy_lons

if (length(params$deploy_lons) == 4 & params$deploy_lons[1] == "-160") {
  cpal <- c("#4E79A7", "#F28E2B", "#76B7B2", "#E15759")
} else if (length(params$deploy_lons) == 3 & params$deploy_lons[1] == "-150") {
  cpal <- c("#F28E2B", "#76B7B2", "#E15759")
} else {
  # otherwise, assign colors by n = deploy_lons
  pal <- ggthemes::ggthemes_data[["tableau"]][["color-palettes"]][["regular"]][[1]]$value 

  color.gradient <- function(x, colors = pal, colsteps = length(params$deploy_lons)) {
    return(colorRampPalette(colors)(colsteps)[findInterval(x, seq(min(x), max(x), length.out = colsteps))])
  }
  cpal <- color.gradient(1:length(params$deploy_lons))
}

```

```{r extract-xy-from-rasters}

xtract_df_long <- get_timeseries(rasIn = ras, pts2extract = xy, subset_dt = getZ(ras)) %>%
  mutate(lon = ceiling(lon))

```

```{r set-timeseries-dt-interval}
if(params$interval == 'daily'){
    df <- xtract_df_long %>% 
          mutate(ID = str_c(abs(lon), '°W')) 
    
} else if(params$interval == 'weekly'){
    
    df <- xtract_df_long %>%
        mutate(end_of_week = ceiling_date(date, "week") %>% as.Date(.)) %>%
        group_by(end_of_week, ID, lon, lat) %>%
        summarize(value = mean(value, na.rm = TRUE), .groups = "drop") %>%
        rename('date' = 'end_of_week')
}

```

```{r save-rds, eval=params$save_rds}
saveRDS(df, file="../data/weekly_sst_df.rds")

```



```{r ggplot-xy-timeseries}
# plot 
p_sst_ts <- plot_timeseries(data = df %>% 
                              mutate(ID = str_c(abs(ceiling(lon)), ' W')), 
                            cpal = cpal, ylimits = c(6,20), ybreaks = seq(6,20, by = 2)) +
    # 
    geom_rect(aes(ymin = 16.9, ymax = 17.1,
                            xmin = date[1], xmax = date[length(date)]), fill='gray10',
            alpha = 0.15, inherit.aes = FALSE) +

    # geom_hline(yintercept = params$sst_thresh, linetype = 2, colour = "azure4") +
  scale_colour_manual(values=cpal, name = "Longitude ( W)") +
  labs(x="Date", y="Sea surface temperature (°C)") +
  # theme(legend.direction="horizontal",legend.position="top", legend.box = "vertical")+
    NULL

```

```{r add-clims, eval=params$add_clim}
# load clim rds
# longterm_sst_mday_df <- readRDS(file='../data/longterm_sst_mday_df.rds')
longterm_avgs <- readRDS(file='../data/longterm_avgs_sst_mday.rds')
# source('add_clims.R')

longterm_df <- df %>%
  select(c("ID", "lon", "lat", "date")) %>%
  mutate(month = month(date),
         lon = ceiling(lon),
         lonID = str_c(abs(lon), '°W')) %>%
  left_join(., longterm_avgs, by =c('ID', 'month')) %>%
  rename("value" = "longterm_avg") 

longterm_df_formatted <- longterm_df %>%
  mutate(ID = str_c(abs(lon), ' W')) %>%
  mutate(ID = as.factor(ID))



## plot
p_longterm_sst_ts <-  p_sst_ts + 
  # geom_hline(yintercept = 17, linetype = 2, colour = "black") +
  geom_line(data = longterm_df_formatted, aes(group = ID, color = factor(lon)), linewidth = 1, alpha = 0.5) + 
  scale_colour_manual(values=cpal, name = "Longitude (°W)") +
  labs(x="Date", y="Sea surface temperature (°C)") +
  # theme(legend.direction="horizontal",legend.position="top", legend.box = "vertical")+
  theme(legend.position = "none") +
  facet_wrap(~ID, ncol=1)



```


```{r}
title = '' #str_c("\nAverage", str_to_title(params$interval), str_to_upper(params$eov), "along shipping route \n", sep = " ")
subtitle = '' #str_c(str_to_upper(params$eov), "colors correspond to color locations on map for near real-time SST (darker dotted-line) \nand long-term climatology (lighter solid line)", sep = " ")
  
sst_plot <- p_longterm_sst_ts +
  labs(
    title = title,
    subtitle = subtitle,
    caption = "Source:\nNOAA Coral Reef Watch, 5-km Daily SST (weekly averages) and Monthly SST (long-term averages)",
    x = "Date", y = str_c(str_to_upper(params$eov), " (", params$eov_unit, ")\n", sep = ""),
    colour = "Longitude (°W)"
  )


```

```{r add-sst-raster, eval=params$add_sst_map}
library(raster)
library(leaflet)
library(leaflet.extras2)

# get most recent daily sst raster. subtract enddate by 1 since in NZ time
enddate_ras = subset(ras, which(getZ(ras) == (params$enddate - 1)))
pal_rev <- colorNumeric(c("#2c7bb6","#abd9e9","#ffffbf","#fdae61", "#d7191c"), values(enddate_ras), reverse = FALSE, na.color = "transparent")

ras_contour_17C = rasterToContour(enddate_ras, levels=17)

coords_17C <- ras_contour_17C %>% 
  as(., "SpatialPointsDataFrame") %>%
  as.data.frame(as(., "SpatialPointsDataFrame"))

df_17C <- data.frame(group = c("17"),
                 lat = coords_17C$coords.x2,
                 lng = coords_17C$coords.x1,
                 lng360 = make360(coords_17C$coords.x1)) %>%
      filter(lng360 > 180.5)

```


```{r plot-map}

fig_top <- get_npac_map(xy, lon_type='360', cpal, col_borders=TRUE) %>% 
  addScaleBar(position = "bottomleft", options = scaleBarOptions())

# Add SST daily raster to map
if(params$add_sst_map){
  map <- fig_top %>%
    addRasterImage(enddate_ras, colors = pal_rev, opacity = 0.8) %>%
    addLegend('topright',
              pal = pal_rev,
              values = values(enddate_ras),
              position = "topright",
              title = "SST (°C)",
              labFormat = labelFormat(transform = function(x) sort(x, decreasing = FALSE))) 
  #Add the contour lines as lines on the map
  map <- addCircleMarkers(map, data = df_17C, lng = ~lng360, lat = ~lat, 
                          group = ~group, color = "gray10", radius = 1.5)

} else {
map <- fig_top
}

fig_bottom <- sst_plot

# fig_bottom <- ggplotly(sst_plot, tooltip = c("text"))

```

<br>

### **Figure 1) Map.** <span style="font-size: 16pt">Estimated shipping route (gray) and potential turtle deployment locations (colors) for June 2023.</span>

```{r, eval=params$add_sst_map}
print(str_c('Daily SST map for ', getZ(enddate_ras), '. 17°C isotherm shown in black.'))
```


```{r plot-top-map, fig.height= 2, fig.width = 4, fig.align="center"}
# fig_top 
map
```

<br>

### **Figure 2) Average SST time series.** 
<br>
<span style="font-size: 16pt"> SST colors correspond to color locations on the map for the most recent weekly SST averages in 2023 (darker dotted-line) and long-term SST averages between 1997-2022 (lighter solid line). 
The black horizontal line at 17°C is a reference for optimal temperatures during turtle release.
</span>

```{r, fig.height= 10}
fig_bottom
```


```{r}
print(str_c('publish date-time: ', Sys.time(), ' ', Sys.timezone()))
```

